CRUSE to Safe Cycling in Ireland

### 2023-09-25 paper.qmd
Minor rewording

The results for the other

@@

The CRUSE tool can help both in terms of describing the current situation, and also prioritise investment in those routes lacking infrastructure highlighted by @caulfield2012 as being least favoured by cyclists.

>>>>

<!-- The results for the other -->

@@

The CRUSE tool can help both in terms of describing the current situation, and also prioritise investment in those direct routes with high cycling potential that lack adequate cycling infrastructure, highlighted by @caulfield2012.
